
\section{Model components}
\label{chap:model_components}
The previous presented equations served to calculate the profit to be maximized.
BUt, there are fundamental real-world components that must be reflected in our model,
which impose constraints on the profit-maximizing formulations.

We begin by examining the battery system and its charging capabilities in more detail.
Subsequently, the modeling of the grid connection point is discussed.

\subsection{Battery \& Charging Capabilities}
The fundamental properties of the battery storage are described through parameters combined with constraints.
The battery storage has a maximum charging and discharging reate $r$ and a maximum capacity $batCap$.
The battery status $BatStat$ is recalculated every quarter-hour and can be found in equation~\ref{eq:BatStat}.
Since the recharge amount $Q_{reload}$, which comes from the wind park, is calculated hourly,
it must be converted to quarter-hourly values. The battery status for the timestep $t_{quarter} + 1$
is derived from the battery status at the previous timestep $t_{quarter}$, along with the actual negative reserve energy delivered,
minus the actual positive reserve energy delivered. Furthermore, there is the option for a working point adjustment $WP$.
This adjustment can be made to align the battery's charge level with the obligations that need to be met.

\begin{alignat}{3}
	BatStat(t_{quarter} + 1)  = BatStat(t_{quarter}) + & \frac{1}{4} Q_{reload}(t_{hour})\notag                                                               \\
	                                                   & +\sum_{s_{RA}}1/|s_{RA}|  * Q^{in}_{RA}(t_{quarter}, s_{RA})\notag                                   \\
	                                                   & - \sum_{s_{RA}}1/|s_{RA}|  * Q^{out}_{RA}(t_{quarter}, s_{RA})\notag                                 \\
	                                                   & - \sum_{s_{RA}}1/|s_{RA}|  * WP_{out}(t_{quarter}, s_{RA})\notag                                     \\
	                                                   & + \sum_{s_{RA}}1/|s_{RA}|  * WP_{in}(t_{quarter}, s_{RA})\notag                                      \\
	                                                   & \forall t_{quarter}, t_{hour} = \left\lfloor \frac{t_{quarter}}{4} \right\rfloor  \label{eq:BatStat} \\
	0 \leq  BatStat                                    & (t_{quarter}) 			\label{eq:BatStat_nonNeg}                                                           \\
	BatStat(t_{quarter}) \leq  batCap                  & \label{eq:BatStat_cap}
\end{alignat}


\subsection{Grid Connection}
The wind farm and the battery storage system
share a common grid connection. As a result, their combined output is subject to
a maximum power constraint, which must be respected throughout the optimization process.
The maximum power that can flow through the connection point is $a$. This power limit applies in both directions,
as shown in equations \ref{eq:a_general_pos} and \ref{eq:a_general_neg}. Since this constraint applies to all quarter-hour
intervals, we have to divide the work of the wind farm and the grid connection maximum power by four. The $strictFactor$ describes a binary parameter
that can be set to either 0 or 1.
When set to 0, the parameter is considered active,
meaning that power contributions in the opposite direction
do not relax the corresponding constraint.
For subsequent calculations, this factor is always assumed to be active.

\begin{alignat}{3}
	\frac{a}{4} + strictFactor * (Q^{in}_{RA}(t_{quarter}, s_{RA}) +  WP_{in}(t_{quarter}, s_{RA})) \notag                                  \\
	\geq \frac{1}{4} Q_{DA}(t_{hour})  + Q^{out}_{RA}(t_{quarter}, s_{RA}) + WP_{out}(t_{quarter}, s_{RA}) \notag                           \\
	\quad \forall s_{RA},  t_{quarter},  t_{hour} = \left\lfloor \frac{t_{quarter}}{4}\right\rfloor\label{eq:a_general_pos}                 \\
	\frac{a}{4} + strictFactor * ( \frac{1}{4}Q_{DA}(t_{hour}) +  Q^{out}_{RA}(t_{quarter}, s_{RA}) + WP_{out}(t_{quarter}, s_{RA}) )\notag \\
	\geq Q^{in}_{RA}(t_{quarter}, s_{RA}) +  WP_{in}(t_{quarter}, s_{RA}) \notag                                                            \\
	\quad \forall s_{RA},  t_{quarter},  t_{hour} = \left\lfloor \frac{t_{quarter}}{4}\right\rfloor \label{eq:a_general_neg}
\end{alignat}
